Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2022-11-14 rmd/manuscript.Rmd
edit

@@

No data were used or produced in this research. R functions for simulations are provided as the R package mcbrnet version 1.2.3 (available at [\<https://github.com/aterui/mcbrnet\>](https://github.com/aterui/mcbrnet){.uri}). Codes for simulations, statistical analysis, figures, and tables are available at [\<https://github.com/aterui/public-proj_fcl-river-theory\>](https://github.com/aterui/public-proj_fcl-river-theory){.uri}.

>>>>

No data were used or produced in this research. R functions for simulations are provided as the R package mcbrnet version 1.2.3 (available at <https://github.com/aterui/mcbrnet>). Codes for simulations, statistical analysis, figures, and tables are available at <https://github.com/aterui/public-proj_fcl-river-theory>.

\clearpage

@@
